---
title: "World cities by population"
author: "Maria Ronacher"
date: "7/3/2019"
output: ioslides_presentation
---

## Objective

This tiny Shiny app lets you display all world cities with population in the given range and with a focus on a chosen area.

We had to set the lower limit to 100,000 people due to the memory limitations on the free Shinyapps plan.

## Data

The data on the world cities comes from the [simplemaps.com](https://simplemaps.com/data/world-cities) website. We used the Basic database. The database was updated in 2019.

```{r}
df <- read.csv("worldcities.csv", sep=",")
colnames(df)
nrow(df[!is.na(df$population), ])
```

## How to use the app

Simply input the range of population using the two-ended slider and select the part of the world you'd like to focus on. The map will update automatically.

## Output

The map will look like this:
```{r, echo=FALSE, message = FALSE}
library(dplyr)
library(leaflet)
df_sub <- df %>% filter(population %in% (5000000:10000000))
mymap <- leaflet(df_sub)
mymap <- mymap %>%
        addTiles() %>%
        setView(lng=16.4365448, 
                lat=2.6112207, 
                zoom=3) %>%
        addMarkers(popup = paste("Country:", df_sub$country, "<br>",
                                 "City:", df_sub$city, "<br>",
                                 "Population:", df_sub$population))
mymap
```
<font size="3">Population range: 5,000,000 - 10,000,000; focus: Africa</font>
